---
title: "R 基礎描述性統計"
author: "Ivan Lin"
date: "2020年4月23日"
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---
# 描述性統計 Descriptive Statistics
當剛拿到資料時，所有資料探勘者直覺會做的第一件事情，不外乎就是使用描述性統計增加對資料的了解。



## 常態分布圖

當資料為正偏分佈,也就是落在左側低分區的人數較多時,QQ圖的資料點就會往左側內凹;<br>
當資料為負偏分佈,也就是落在右側高分區的人數較多時,QQ圖的資料點就會往右側外凸;<br>
當資料為高狹分佈,也就是落在中間中分區的人數較多時,QQ圖的資料點就會呈現S型曲線.<br>

`html_pretty` in the [**prettydoc**](https://github.com/yixuan/prettydoc/)
package is a new output format for creating HTML documents from R Markdown files.
`html_pretty` is more lightweight compared to `html_document`, and is more
stylish than `html_vignette` when creating package vignettes.

## New Styles

`html_pretty` currently supports three page themes (`cayman`, `tactile` and
`architect`), and two syntax highlight styles (`github` and `vignette`).
The theme and highlight styles can be specified in the document metadata,
for example:

```yaml
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
```

## Your Familiar Tools

Feel free to use the `knitr` infrastructure with dozens of tunable options in
your document.

```{r fig.width=6, fig.height=6, fig.align='center'}
set.seed(123)
n <- 1000
x1  <- matrix(rnorm(n), ncol = 2)
x2  <- matrix(rnorm(n, mean = 3, sd = 1.5), ncol = 2)
x   <- rbind(x1, x2)
head(x)
smoothScatter(x, xlab = "x1", ylab = "x2")
```

You can include code snippets of languages other than R, but note that
the block header has no curly brackets around the language name.

```cpp
// [[Rcpp::export]]
NumericVector timesTwo(NumericVector x) {
    return x * 2;
}
```

You can also write math expressions, e.g. $Y = X\beta + \epsilon$,
footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(iris, 10))
```

## Stay Tuned

Please visit the [development page](https://github.com/yixuan/prettydoc/) of the 
`prettydoc` package for latest updates and news. Comments, bug reports and
pull requests are always welcome.
